Research Report

### 2023-03-03 tex/paper-acts/main.tex
Add plots of run time per trial.

\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Optimizer score per trial..}

@@

@@

@@

@@

>>>>

\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/score.png}{Optimizer score per trial.}
\figpic{6cm}{/home/user1/time/2023-02-21/2023-02-21-23-06-52/time.png}{Optimizer time per trial.}

@@

\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-18-01-01/time.png}{Optimizer time per trial.}

@@

\figpic{6cm}{/home/user1/time/2023-02-22/2023-02-22-21-04-06/time.png}{Optimizer time per trial.}

@@

\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-05-10-03/time.png}{Optimizer time per trial.}

@@

\figpic{6cm}{/home/user1/time/2023-02-23/2023-02-23-12-34-56/time.png}{Optimizer time per trial.}
